Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from biclaR

### 2024-05-06 paper/PaperCEUS/PaperCEUS_rev1.Rmd
percentages in trips - still to conclude

  #CONTINUE FROM HERE ---  LOOK AT DIFRERENCES TOTAL AND VIAGENS
ENMAC4 = 0.04 # 4%
ENMAC10 = 0.10 # 10#
CAR_PT_TRANSF_mun_or_geo_18 = CAR_PT_TRANSF_mun_or_geo_18 |> 
  mutate(Bikeper = Bike / viagens) |>  #should it be "viagens" or "Total  -- all trips, not only the found ones
  mutate(Bike_new4 = ifelse(Bikeper >= ENMAC4*100, Bike, ENMAC4 * viagens),
         Bike_new10 = ifelse(Bikeper >= ENMAC10*100, Bike, ENMAC10 * viagens)) |> 
  mutate(Bike4 = ifelse(Bikeper >= ENMAC4*100, Bike, Bike + Bike_new4),
         Bike10 = ifelse(Bikeper >= ENMAC10*100, Bike, Bike + Bike_new10),
         Car_4 = ifelse(Bikeper >= ENMAC4*100, Car, Car - Bike_new4),
         Car_10 = ifelse(Bikeper >= ENMAC10*100, Car, Car - Bike_new10),
         TP_4 = TP + Bike_new4,
         TP_10 = TP + Bike_new10) |> 
  mutate(Bike_new4per = 100*Bike_new4 / viagens,
         Bike_new10per = 100*Bike_new10 / viagens,
         TPper = 100*TP / viagens,
         TP_4per = 100*TP_4 / viagens,
         TP_10per = 100*TP_10 / viagens)

>>>>

ENMAC4 = 0.04 # 4%
ENMAC10 = 0.10 # 10#
CAR_PT_TRANSF_mun_or_geo_18 = CAR_PT_TRANSF_mun_or_geo_18 |> 
  mutate(Bikeper = Bike / viagens,
         Carper = Car / viagens) |>  #should it be "viagens" or "Total  -- all trips, not only the found ones
  mutate(Bike_new4 = ifelse(Bikeper >= ENMAC4 | Carper <= ENMAC4, Bike, ENMAC4 * viagens),
         Bike_new10 = ifelse(Bikeper >= ENMAC10 | Carper <= ENMAC4, Bike, ENMAC10 * viagens)) |> 
  mutate(Bike4 = ifelse(Bikeper >= ENMAC4 | Carper <= ENMAC4, Bike, Bike + Bike_new4),
         Bike10 = ifelse(Bikeper >= ENMAC10 | Carper <= ENMAC4, Bike, Bike + Bike_new10),
         Car_4 = ifelse(Bikeper >= ENMAC4 | Carper <= ENMAC4, Car, Car - Bike_new4),
         Car_10 = ifelse(Bikeper >= ENMAC10 | Carper <= ENMAC4, Car, Car - Bike_new10),
         TP_4 = TP + Bike_new4,
         TP_10 = TP + Bike_new10) |> 
  mutate(Bike_new4per = 100*Bike_new4 / viagens,
         Bike_new10per = 100*Bike_new10 / viagens,
         TPper = 100*TP / viagens,
         TP_4per = 100*TP_4 / viagens,
         TP_10per = 100*TP_10 / viagens)

  #CONTINUE FROM HERE ---  LOOK AT DIFRERENCES TOTAL AND VIAGENS
